 

### 2020-09-24 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

*Carotinoids* 
-	photoprotective- disseminate heat, acclimate to high T. THese are proportional to irradiance 
-	antioxidant scavenging function- protect against cellular damage
- Königer et. al. 1995, and  Matsubara et al. 2009?

@@

**Many of the biophysical and trait variable reviewed above affect leaf temperature, $T_{leaf}$, which in turn has a strong influence on leaf metabolism (see following section).**
$T_{leaf}$ is determined by the energy balance of a leaf and can be estimated based on basic biophysical principles [@campbell_introduction_1998; @muir_tealeaves_2019] (Fig. 3).
While small leaves remain within a few degrees of $T_{air}$, regardless of stomatal conductance, wider leaves can have temperatures deviating more from air temperature.
Large leaves can be significantly cooler than $T_{air}$ under low radiation with stomata open, and significantly hotter under high radiation with stomata closed.  
Leaves with open stomata and high radiation loads maintain $T_{leaf}$ similar to $T_{air}$, with coolest leaves at intermediate sizes (~10mm).
Shaded understory leaves should tend to maintain cooler daytime leaf temperatures for any given level of stomatal conductance.
However, counteracting this, lower wind speed in understory would reduce latent heat loss.
Thus, under hot conditions, canopy leaves exposed to higher wind speeds would be most effective at cooling when sufficient water is available to maintain high stomatal conductance; however, their $T_{leaf}$ can be highly elevated above $T_{air}$ when stomatal conductance is limiting.

>>>>

*Carotinoids* 
-	photoprotective- disseminate heat, acclimate to high T. THese are proportional to irradiance 
-	antioxidant scavenging function- protect against cellular damage
- Koniger et. al. 1995, and  Matsubara et al. 2009?

@@

**Many of the biophysical and trait variable reviewed above affect leaf temperature, $T_{leaf}$, which in turn has a strong influence on leaf metabolism (see following section).**
$T_{leaf}$ is determined by the energy balance of a leaf and can be estimated based on basic biophysical principles [@campbell_introduction_1998; @muir_tealeaves_2019] (Fig. 3).
While small leaves remain within a few degrees of $T_{air}$, regardless of stomatal conductance, wider leaves can have temperatures deviating more from air temperature.[@fauset_differences_2018]
Large leaves can be significantly cooler than $T_{air}$ under low radiation with stomata open, and significantly hotter under high radiation with stomata closed.  
Leaves with open stomata and high radiation loads maintain $T_{leaf}$ similar to $T_{air}$, with coolest leaves at intermediate sizes (~10mm).
Shaded understory leaves should tend to maintain cooler daytime leaf temperatures for any given level of stomatal conductance.
However, counteracting this, lower wind speed in understory would reduce latent heat loss.
Thus, under hot conditions, canopy leaves exposed to higher wind speeds would be most effective at cooling when sufficient water is available to maintain high stomatal conductance; however, their $T_{leaf}$ can be highly elevated above $T_{air}$ when stomatal conductance is limiting.
